|

### 2018-06-12 paper/Paper.Rmd
Inserting charts; next step is to fix them in Latex

### INSERT FIGURE 1 HERE 
```{r panel stargazer CCI}
stargazer(CCIreg1, CCIreg2, CCIreg3, CCIreg5,
  type="text", 
  title = "Are campaign limits and corruption convictions correlated?",
  out="collateral/CCI.htm",
  dep.var.labels = c("Corruption Convictions Index"),
  covariate.labels=c("Individual limit amounts", "Individual limits (dummy)","Individual-to-party limit amount","Individual-to-party limits (dummy)","PAC limit amounts","PAC limits (dummy)"))
```
The second set of models (below) also fails to find a relationship between state-level campaign contribution limits and media mentions of corruption as measured by the Corruption Reflections Index, with one exception: The presence of limits on what an individual can give to a party is associated with a 0.087 point decline in the Corruption Reflection Index. The Corruption Reflections Index operates on a scale of zero to one (with a few outlying exceptions), meaning that the presence of individual-to-party limits is associated with an 8.7% point decrease in the index.

### INSERT FIGURE 2 HERE 
```{r stargazer CRI}
stargazer(CRIreg1, CRIreg2, CRIreg3, CRIreg5,
  type="text", 
  title = "Are campaign limits and corruption reflections correlated?",
  out="collateral/CRI.htm",
  dep.var.labels = c("Corruption Reflections Index"),
  covariate.labels=c("Individual limit amounts", "Individual limits (dummy)","Individual-to-party limit amount","Individual-to-party limits (dummy)","PAC limit amounts","PAC limits (dummy)"))

# stargazer(CCIreg1, CCIreg2, CCIreg3, CCIreg5, CRIreg1, CRIreg2, CRIreg3, CRIreg5,
#   type="text", 
#   out="collateral/CCICRI.htm",
#   dep.var.labels = c("Corruption Convictions Index", "Corruption Reflections Index"),
#   covariate.labels=c("Individual limit amounts", "Individual limits (dummy)","Individual-to-party limit amount","Individual-to-party limits (dummy)","PAC limit amounts","PAC limits (dummy)"))
```

@@

### INSERT FIGURE 3 HERE 
```{r stargazer controlled panel}
stargazer(CCIcontrol01,CCIcontrol02,CRIcontrol01,CRIcontrol02,
  type="text", 
  out="collateral/CCICRIcontrol.htm",
  dep.var.labels = c("Corruption Convictions Index", "Corruption Reflections Index"),
  covariate.labels=c("Divided government", "Binding one-term limit"," Binding two-term limit","Real per capita income ($1000)","AUSAs per million population","Unemployment","Citizen ideology measure","Percent high school graduates","Real per capita gov revenues ($1000)","Inequality: Male wages","Relative government wages","Urbanization","Log of population (millions)","Individual limit amounts", "Individual limits (dummy)","Individual-to-party limit amount","Individual-to-party limits (dummy)","PAC limit amounts","PAC limits (dummy)")
  )
```

@@

>>>>

```{r stargzer CCI html}
stargazer(CCIreg1, CCIreg2, CCIreg3, CCIreg5,
  type="text", 
  title = "Are campaign limits and corruption convictions correlated?",
  out="collateral/CCI.htm",
  dep.var.labels = c("Corruption Convictions Index"),
  covariate.labels=c("Individual limit amounts", "Individual limits (dummy)","Individual-to-party limit amount","Individual-to-party limits (dummy)","PAC limit amounts","PAC limits (dummy)"))
```

```{r stargazer CCI latex, results="asis", include=F}
stargazer(CCIreg1, CCIreg2, CCIreg3, CCIreg5,
  type="latex", 
  title = "Are campaign limits and corruption convictions correlated?",
  dep.var.labels = c("Corruption Convictions Index"),
  covariate.labels=c("Individual limit amounts", "Individual limits (dummy)","Individual-to-party limit amount","Individual-to-party limits (dummy)","PAC limit amounts","PAC limits (dummy)"))
```

\begin{table}[!htbp] \centering 
  \caption{Are campaign limits and corruption convictions correlated?} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lcccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{4}{c}{\textit{Dependent variable:}} \\ 
\cline{2-5} 
\\[-1.8ex] & \multicolumn{4}{c}{Corruption Convictions Index} \\ 
\\[-1.8ex] & (1) & (2) & (3) & (4)\\ 
\hline \\[-1.8ex] 
 Individual limit amounts & $-$0.00004 &  &  & $-$0.00003 \\ 
  & (0.00005) &  &  & (0.0001) \\ 
  & & & & \\ 
 Individual limits (dummy) & $-$4.021 &  &  & $-$2.989 \\ 
  & (4.572) &  &  & (5.076) \\ 
  & & & & \\ 
 Individual-to-party limit amount &  & $-$0.00000 &  & 0.00000 \\ 
  &  & (0.00001) &  & (0.00001) \\ 
  & & & & \\ 
 Individual-to-party limits (dummy) &  & $-$0.019 &  & 0.363 \\ 
  &  & (0.626) &  & (0.684) \\ 
  & & & & \\ 
 PAC limit amounts &  &  & $-$0.00002 & $-$0.00002 \\ 
  &  &  & (0.00002) & (0.00002) \\ 
  & & & & \\ 
 PAC limits (dummy) &  &  & $-$1.762 & $-$1.339 \\ 
  &  &  & (1.519) & (1.743) \\ 
  & & & & \\ 
\hline \\[-1.8ex] 
Observations & 1,149 & 1,149 & 1,149 & 1,149 \\ 
R$^{2}$ & 0.002 & 0.00002 & 0.002 & 0.002 \\ 
Adjusted R$^{2}$ & $-$0.066 & $-$0.068 & $-$0.066 & $-$0.069 \\ 
F Statistic & 0.826 (df = 2; 1075) & 0.012 (df = 2; 1075) & 0.843 (df = 2; 1075) & 0.426 (df = 6; 1071) \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{4}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table}

The second set of models (below) also fails to find a relationship between state-level campaign contribution limits and media mentions of corruption as measured by the Corruption Reflections Index, with one exception: The presence of limits on what an individual can give to a party is associated with a 0.087 point decline in the Corruption Reflection Index. The Corruption Reflections Index operates on a scale of zero to one (with a few outlying exceptions), meaning that the presence of individual-to-party limits is associated with an 8.7% point decrease in the index.

```{r stargazer CRI html}
stargazer(CRIreg1, CRIreg2, CRIreg3, CRIreg5,
  type="text", 
  title = "Are campaign limits and corruption reflections correlated?",
  out="collateral/CRI.htm",
  dep.var.labels = c("Corruption Reflections Index"),
  covariate.labels=c("Individual limit amounts", "Individual limits (dummy)","Individual-to-party limit amount","Individual-to-party limits (dummy)","PAC limit amounts","PAC limits (dummy)"))
```

```{r stargazer CRI latex, results="asis", include=F}
stargazer(CRIreg1, CRIreg2, CRIreg3, CRIreg5,
  title = "Are campaign limits and corruption reflections correlated?",
  dep.var.labels = c("Corruption Reflections Index"),
  covariate.labels=c("Individual limit amounts", "Individual limits (dummy)","Individual-to-party limit amount","Individual-to-party limits (dummy)","PAC limit amounts","PAC limits (dummy)"))
```

\begin{table}[!htbp] \centering 
  \caption{Are campaign limits and corruption reflections correlated?} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lcccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{4}{c}{\textit{Dependent variable:}} \\ 
\cline{2-5} 
\\[-1.8ex] & \multicolumn{4}{c}{Corruption Reflections Index} \\ 
\\[-1.8ex] & (1) & (2) & (3) & (4)\\ 
\hline \\[-1.8ex] 
 Individual limit amounts & $-$0.00000 &  &  & $-$0.00000 \\ 
  & (0.00000) &  &  & (0.00000) \\ 
  & & & & \\ 
 Individual limits (dummy) & $-$0.316 &  &  & $-$0.328 \\ 
  & (0.257) &  &  & (0.284) \\ 
  & & & & \\ 
 Individual-to-party limit amount &  & $-$0.00000 &  & $-$0.00000 \\ 
  &  & (0.00000) &  & (0.00000) \\ 
  & & & & \\ 
 Individual-to-party limits (dummy) &  & $-$0.087$^{**}$ &  & $-$0.099$^{***}$ \\ 
  &  & (0.035) &  & (0.038) \\ 
  & & & & \\ 
 PAC limit amounts &  &  & 0.00000 & 0.00000 \\ 
  &  &  & (0.00000) & (0.00000) \\ 
  & & & & \\ 
 PAC limits (dummy) &  &  & 0.009 & 0.096 \\ 
  &  &  & (0.085) & (0.098) \\ 
  & & & & \\ 
\hline \\[-1.8ex] 
Observations & 1,150 & 1,150 & 1,150 & 1,150 \\ 
R$^{2}$ & 0.002 & 0.007 & 0.0001 & 0.010 \\ 
Adjusted R$^{2}$ & $-$0.066 & $-$0.060 & $-$0.068 & $-$0.061 \\ 
F Statistic & 0.842 (df = 2; 1076) & 3.937$^{**}$ (df = 2; 1076) & 0.037 (df = 2; 1076) & 1.858$^{*}$ (df = 6; 1072) \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{4}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table}

@@

```{r stargazer controlled panel}
stargazer(CCIcontrol01,CCIcontrol02,CRIcontrol01,CRIcontrol02,
  type="text", 
  out="collateral/CCICRIcontrol.htm",
  dep.var.labels = c("Corruption Convictions Index", "Corruption Reflections Index"),
  covariate.labels=c("Divided government", "Binding one-term limit"," Binding two-term limit","Real per capita income ($1000)","AUSAs per million population","Unemployment","Citizen ideology measure","Percent high school graduates","Real per capita gov revenues ($1000)","Inequality: Male wages","Relative government wages","Urbanization","Log of population (millions)","Individual limit amounts", "Individual limits (dummy)","Individual-to-party limit amount","Individual-to-party limits (dummy)","PAC limit amounts","PAC limits (dummy)")
  )
```

```{r stargazer controlled panel latex, results="asis", include=F}
stargazer(CCIcontrol01,CCIcontrol02,CRIcontrol01,CRIcontrol02,
  dep.var.labels = c("Corruption Convictions Index", "Corruption Reflections Index"),
  covariate.labels=c("Divided government", "Binding one-term limit"," Binding two-term limit","Real per capita income (thousands)","AUSAs per million population","Unemployment","Citizen ideology measure","Percent high school graduates","Real per capita gov revenues (thousands)","Inequality: Male wages","Relative government wages","Urbanization","Log of population (millions)","Individual limit amounts", "Individual limits (dummy)","Individual-to-party limit amount","Individual-to-party limits (dummy)","PAC limit amounts","PAC limits (dummy)")
  )
```

Too big to include?

\begin{table}[!htbp] \centering 
  \caption{} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lcccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{4}{c}{\textit{Dependent variable:}} \\ 
\cline{2-5} 
\\[-1.8ex] & \multicolumn{2}{c}{Corruption Convictions Index} & \multicolumn{2}{c}{Corruption Reflections Index} \\ 
\\[-1.8ex] & (1) & (2) & (3) & (4)\\ 
\hline \\[-1.8ex] 
 Divided government & $-$0.371$^{*}$ & $-$0.332 & 0.012 & 0.014 \\ 
  & (0.208) & (0.211) & (0.014) & (0.014) \\ 
  & & & & \\ 
 Binding one-term limit & 0.228 & $-$0.294 & 0.056 & 0.112 \\ 
  & (1.399) & (1.494) & (0.093) & (0.098) \\ 
  & & & & \\ 
  Binding two-term limit & 0.013 & 0.048 & 0.002 & $-$0.0004 \\ 
  & (0.232) & (0.234) & (0.015) & (0.015) \\ 
  & & & & \\ 
 Real per capita income (thousands) & $-$0.001$^{**}$ & $-$0.001$^{**}$ & 0.00001 & 0.00001 \\ 
  & (0.0002) & (0.0002) & (0.00002) & (0.00002) \\ 
  & & & & \\ 
 AUSAs per million population & 0.064 & 0.077 & 0.0003 & $-$0.001 \\ 
  & (0.060) & (0.061) & (0.004) & (0.004) \\ 
  & & & & \\ 
 Unemployment & 0.007 & 0.029 & 0.015 & 0.013 \\ 
  & (0.155) & (0.161) & (0.010) & (0.011) \\ 
  & & & & \\ 
 Citizen ideology measure & $-$0.001 & 0.001 & $-$0.001 & $-$0.001 \\ 
  & (0.020) & (0.021) & (0.001) & (0.001) \\ 
  & & & & \\ 
 Percent high school graduates & $-$2.187 & $-$1.955 & $-$0.707 & $-$0.901$^{*}$ \\ 
  & (7.236) & (7.455) & (0.477) & (0.488) \\ 
  & & & & \\ 
 Real per capita gov revenues (thousands) & 0.002 & 0.002$^{*}$ & 0.0002$^{**}$ & 0.0002$^{***}$ \\ 
  & (0.001) & (0.001) & (0.0001) & (0.0001) \\ 
  & & & & \\ 
 Inequality: Male wages & 0.131$^{***}$ & 0.125$^{***}$ & $-$0.004 & $-$0.003 \\ 
  & (0.048) & (0.048) & (0.003) & (0.003) \\ 
  & & & & \\ 
 Relative government wages & 32.384 & 28.128 & 4.163 & 7.262$^{**}$ \\ 
  & (45.126) & (47.558) & (2.984) & (3.123) \\ 
  & & & & \\ 
 Urbanization & 0.074 & 0.073 & $-$0.013$^{*}$ & $-$0.016$^{**}$ \\ 
  & (0.114) & (0.115) & (0.007) & (0.008) \\ 
  & & & & \\ 
 Log of population (millions) & 3.883 & 2.988 & 0.098 & 0.018 \\ 
  & (3.032) & (3.231) & (0.200) & (0.212) \\ 
  & & & & \\ 
 Individual limit amounts &  & 0.0001 &  & $-$0.00001 \\ 
  &  & (0.0001) &  & (0.00001) \\ 
  & & & & \\ 
 Individual limits (dummy) &  & 8.012 &  & $-$0.561 \\ 
  &  & (8.409) &  & (0.550) \\ 
  & & & & \\ 
 Individual-to-party limit amount &  & 0.00000 &  & 0.00000 \\ 
  &  & (0.00001) &  & (0.00000) \\ 
  & & & & \\ 
 Individual-to-party limits (dummy) &  & 0.260 &  & $-$0.111$^{**}$ \\ 
  &  & (0.744) &  & (0.049) \\ 
  & & & & \\ 
 PAC limit amounts &  & $-$0.00002 &  & $-$0.00000 \\ 
  &  & (0.00004) &  & (0.00000) \\ 
  & & & & \\ 
 PAC limits (dummy) &  & $-$1.547 &  & $-$0.192 \\ 
  &  & (3.176) &  & (0.209) \\ 
  & & & & \\ 
\hline \\[-1.8ex] 
Observations & 671 & 671 & 672 & 672 \\ 
R$^{2}$ & 0.038 & 0.043 & 0.029 & 0.047 \\ 
Adjusted R$^{2}$ & $-$0.080 & $-$0.084 & $-$0.090 & $-$0.080 \\ 
F Statistic & 1.818$^{**}$ (df = 13; 597) & 1.413 (df = 19; 591) & 1.368 (df = 13; 598) & 1.549$^{*}$ (df = 19; 592) \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{4}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table}

@@

```{r stargazer DiD latex, results="asis", include=F}
stargazer(CCIDID01, CCIDID02, CCIDID03, CRIDID01, CRIDID02, CRIDID03,
  title = "Do changes in limits lead to lower levels of corruption?",
  dep.var.labels = c("Corruption Convictions Index", "Corruption Reflections Index"),
  covariate.labels=c("Individual limits removed","Individual limits imposed","Individual limit amount","Individual limits removed*amount","Individual limits imposed*amount",
                     "PAC limits removed","PAC limits imposed","PAC limit amount","PAC limits removed*amount","PAC limits imposed*amount",
                     "Individual-to-party limits removed","Individual-to-party limits imposed","Individual-to-party limit amount","Individual-to-party limits removed*amount","Individual-to-party limits imposed*amount"))

\begin{table}[!htbp] \centering 
  \caption{Do changes in limits lead to lower levels of corruption?} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lcccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{6}{c}{\textit{Dependent variable:}} \\ 
\cline{2-7} 
\\[-1.8ex] & \multicolumn{3}{c}{Corruption Convictions Index} & \multicolumn{3}{c}{Corruption Reflections Index} \\ 
\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6)\\ 
\hline \\[-1.8ex] 
 Individual limits removed & 27.590 &  &  & $-$3.567 &  &  \\ 
  & (117.102) &  &  & (7.717) &  &  \\ 
  & & & & & & \\ 
 Individual limits imposed & 4.038 &  &  & 1.324 &  &  \\ 
  & (25.993) &  &  & (1.713) &  &  \\ 
  & & & & & & \\ 
 Individual limit amount & 0.00001 &  &  & 0.00001 &  &  \\ 
  & (0.0001) &  &  & (0.00001) &  &  \\ 
  & & & & & & \\ 
 Individual limits removed*amount & $-$0.0003 &  &  & 0.00003 &  &  \\ 
  & (0.001) &  &  & (0.0001) &  &  \\ 
  & & & & & & \\ 
 Individual limits imposed*amount & 0.00004 &  &  & 0.00000 &  &  \\ 
  & (0.0003) &  &  & (0.00002) &  &  \\ 
  & & & & & & \\ 
 PAC limits removed &  & $-$4.699 &  &  & $-$1.586 &  \\ 
  &  & (42.691) &  &  & (2.815) &  \\ 
  & & & & & & \\ 
 PAC limits imposed &  & $-$0.977 &  &  & 0.129 &  \\ 
  &  & (2.786) &  &  & (0.184) &  \\ 
  & & & & & & \\ 
 PAC limit amount &  & $-$0.00001 &  &  & $-$0.00000 &  \\ 
  &  & (0.0001) &  &  & (0.00000) &  \\ 
  & & & & & & \\ 
 PAC limits removed*amount &  & 0.0001 &  &  & 0.00002 &  \\ 
  &  & (0.0004) &  &  & (0.00003) &  \\ 
  & & & & & & \\ 
 PAC limits imposed*amount &  & 0.00000 &  &  & 0.00000 &  \\ 
  &  & (0.0001) &  &  & (0.00001) &  \\ 
  & & & & & & \\ 
 Individual-to-party limits removed &  &  & $-$1.944 &  &  & 0.044 \\ 
  &  &  & (3.317) &  &  & (0.219) \\ 
  & & & & & & \\ 
 Individual-to-party limits imposed &  &  & $-$0.252 &  &  & 0.010 \\ 
  &  &  & (1.133) &  &  & (0.075) \\ 
  & & & & & & \\ 
 Individual-to-party limit amount &  &  & $-$0.00001 &  &  & $-$0.00000 \\ 
  &  &  & (0.00002) &  &  & (0.00000) \\ 
  & & & & & & \\ 
 Individual-to-party limits removed*amount &  &  &  &  &  &  \\ 
  &  &  &  &  &  &  \\ 
  & & & & & & \\ 
 Individual-to-party limits imposed*amount &  &  & 0.00000 &  &  & 0.00000 \\ 
  &  &  & (0.00002) &  &  & (0.00000) \\ 
  & & & & & & \\ 
 Constant & 3.198$^{***}$ & 3.196$^{***}$ & 3.184$^{***}$ & 0.291$^{***}$ & 0.291$^{***}$ & 0.291$^{***}$ \\ 
  & (0.090) & (0.090) & (0.089) & (0.006) & (0.006) & (0.006) \\ 
  & & & & & & \\ 
\hline \\[-1.8ex] 
Observations & 1,099 & 1,099 & 1,099 & 1,100 & 1,100 & 1,100 \\ 
R$^{2}$ & 0.001 & 0.001 & 0.003 & 0.003 & 0.002 & 0.001 \\ 
Adjusted R$^{2}$ & $-$0.004 & $-$0.004 & $-$0.001 & $-$0.001 & $-$0.003 & $-$0.003 \\ 
Residual Std. Error & 2.939 (df = 1093) & 2.939 (df = 1093) & 2.935 (df = 1094) & 0.194 (df = 1094) & 0.194 (df = 1094) & 0.194 (df = 1095) \\ 
F Statistic & 0.172 (df = 5; 1093) & 0.111 (df = 5; 1093) & 0.691 (df = 4; 1094) & 0.706 (df = 5; 1094) & 0.413 (df = 5; 1094) & 0.217 (df = 4; 1095) \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{6}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table}
